### 2019-07-18 manuscript/discussion.tex
- fixing bad parentheses/spacing

Other lines of evidence about the prevalence of diploidization within Solanaceae or its ancestors are mixed or even conflicting.
% Part I: evidence for WGD in/near family
On the one hand, polyploidy may have occurred prior to the origin of Solanaceae, rendering all extant `diploids' secondarily derived.
\Citet{ku2000} and \citet{blanc2004} posited that the lineage leading to cultivated tomato, \emph{Solanum lycopersicum}, may have experienced one or more whole genome duplications.
A subsequent analysis of synteny between grape and \emph{Solanum} genomes, as well as genetic distances (Ks) between inferred paralogs within genomes of \emph{Solanum} (tomato and potato), each suggested that this lineage experienced a likely round of ancient genome duplication or triplication ( $71 \pm 19$ My, \citet{tomato2012})  likely pre-dating the origin of the family ($49 \pm 3$ My; \citealt{sarkinen_2013}).

>>>>

Other lines of evidence about the prevalence of diploidization within Solanaceae or its ancestors are mixed or even conflicting.
% Part I: evidence for WGD in/near family
On the one hand, polyploidy may have occurred prior to the origin of Solanaceae, rendering all extant `diploids' secondarily derived.
\Citet{ku2000} and \citet{blanc2004} posited that the lineage leading to cultivated tomato, \emph{Solanum lycopersicum}, may have experienced one or more whole genome duplications.
A subsequent analysis of synteny between grape and \emph{Solanum} genomes, as well as genetic distances (Ks) between inferred paralogs within genomes of \emph{Solanum} (tomato and potato), each suggested that this lineage experienced a likely round of ancient genome duplication or triplication ($71 \pm 19$ My; \citealt{tomato2012})  likely pre-dating the origin of the family ($49 \pm 3$ My; \citealt{sarkinen_2013}).
